### 2018-10-28 Sections/economics_of_the_quantum_internet.tex
minor

\begin{definition}[Static computational return]\index{Static computational return} The static computational return is the classical-equivalent processing power of a user's time-share proportion, \mbox{$1/N_t$}, where the user has a fixed investment of one qubit, whereas the network is allowed to expand over time arbitrarily as $N_t$ (e.g according to a quantum Moore's Law),
\begin{align}
	r_\mathrm{static}(t) &= \frac{f_\mathrm{sc}(N_t)}{N_t}\nonumber\\
	&= \chi_\mathrm{sc}(N_t),
\end{align}
which is equivalent to the collective per-qubit computational power\index{Per-qubit computational power} of the entire network.
\end{definition}

@@

	\begin{flushleft}Static computational return (Sec.~\ref{sec:static_comp_ret})\end{flushleft} & \[r_\mathrm{static}(t) = \frac{f_\mathrm{sc}(N_t)}{N_t}\] & \[1\] & \[{N_t}^{p-1}\] & \[\frac{e^{N_t}}{N_t}\] \\

>>>>

\begin{definition}[Static computational return]\index{Static computational return} The static computational return is the classical-equivalent processing power of a user's time-share proportion (\mbox{$n/N_t$}), where the user has a fixed investment of $n$ qubits, whereas the network is allowed to expand over time arbitrarily as $N_t$ (e.g according to a quantum Moore's Law),
\begin{align}
	r_\mathrm{static}(t) &= \frac{n\cdot f_\mathrm{sc}(N_t)}{N_t}\nonumber\\
	&= n\cdot\chi_\mathrm{sc}(N_t),
\end{align}
which is proportional to the collective per-qubit computational power\index{Per-qubit computational power} of the entire network.
\end{definition}

@@

	\begin{flushleft}Static computational return (Sec.~\ref{sec:static_comp_ret})\end{flushleft} & \[r_\mathrm{static}(t) = n\cdot\chi_\mathrm{sc}(N_t)\] & \[n\] & \[n{N_t}^{p-1}\] & \[\frac{n e^{N_t}}{N_t}\] \\
